%%% Local Variables:
%%% mode: latex
%%% TeX-master: "<none>"
%%% End:

\title{Why to compress?}
\author{Vicente González Ruiz}

\maketitle
\tableofcontents

\section{Why to compress?}
\begin{itemize}
\item
  Data compression can reduce the memory requirements of (almost) any
  kind of information source.
\end{itemize}

\subsubsection{Which data?}\label{which-data}
\begin{itemize}
\item
  Mainly \ldots{} audio, image, and video signals.
\end{itemize}

\subsubsection{Why these sources?}

\begin{itemize}
\item
  After the digitalization of any signal we get a sequence \(s[]\) of
  samples that represent the signal \(s\) with more or less fidelity.
\item
  Usually, \(s[]\) is encoded using PCM (Pulse Code Modulation), in
  which every sample \(s[i]\) is represented with the same number of
  bits.
\item
  Most digital PCM signals are memory demanding. For example, in a CD we
  have a data-rate of
\end{itemize}

\begin{equation}
    (16+16)\frac{\text{bits}}{\text{sample}}\times
    44{.}100\frac{\text{samples}}{\text{second}}=
    1{.}411{.}200\frac{\text{bits}}{\text{second}}.
\end{equation}

\begin{itemize}
\tightlist
\item
  Image and video signals require much more memory.
\end{itemize}

\subsubsection{Lab (audio comparison)}

TO-DO

Compress a WAV audio file to MP3 with LAME at 128 kbps. Decompress to
obtain again a WAV file. Substract the original and the decompressed
WAVs and listen it.

\subsubsection{Lab (image comparison)}
\href{}{}

\subsection{Memory requirements of PCM video}

\begin{itemize}
\item
  In RGB (PCM) video, each color pixel need at least 24 bpp
  (bits/pixel).
\item
  The memory requirements of RGB video are enormous. For example, an
  hour of \(640\times 480\times 25\) Hz true-color of PCM video needs:
\end{itemize}

\begin{equation}
    25\frac{\text{images}}{\text{second}}\times
    640\cdot 480\frac{\text{pixels}}{\text{image}}\times
    24\frac{\text{bits}}{\text{pixel}}=
    184{.}320{.}000\frac{\text{bits}}{\text{second}}
\end{equation}

\begin{equation}
    184{.}320{.}000\frac{\text{bits}}{\text{second}} \times
    3{.}600\frac{\text{seconds}}{\text{hour}} \times
    \frac{1~\text{G}}{1{.}024^3}\times
    \frac{1~\text{byte}}{8~\text{bits}} \approx
    77~\text{Gbytes}
\end{equation}

\begin{itemize}
\tightlist
\item
  Video coding techniques should be used to compress this data. Most of
  these techniques are bases on Block-based Motion Estimation.
\end{itemize}

